---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# senso: An Interface to the Philippine Census of Population and Housing Data

<!-- badges: start -->
<!-- badges: end -->

The Philippine Statistics Authority (PSA) makes census of population and housing data publicly available through various data publications and releases over time via their website. This package provides utilities for accessing and processing the census of population and housing data released by the PSA.

## What does `senso` do?

Please note that `senso` is still highly experimental and is undergoing a lot of development. Hence, any functionalities described below and in the rest of the package documentation have a high likelihood of changing interface or approach as we aim for a stable working version.

Currently, the package's main functionalities are:

* Retrieval and/or download of census of population and housing data for every census conducted released by the PSA on their website;

* Standardised naming of census of population and housing statistical table files;

* Upload and/or archive raw census of population and housing data releases onto specific platforms; and,

* Process raw census of population and housing data releases into machine-readable and relational database-ready structures.

## Installation

`senso` is not yet on CRAN but can be installed from the [panukatan R universe](https://panukatan.r-universe.dev) as follows:

```{r install-r-universe, eval = FALSE}
install.packages(
  "senso",
  repos = c('https://panukatan.r-universe.dev', 'https://cloud.r-project.org')
)
```

## Usage

## Citation

If you find the `senso` package useful please cite using the suggested citation provided by a call to the `citation()` function as follows:

```{r citation}
citation("senso")
```

## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/panukatan/senso/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://panukatan.io/senso/CONTRIBUTING.html).

This project is released with a [Contributor Code of Conduct](https://panukatan.io/senso/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.

